Methods and Results

### 2022-10-12 ms.Rmd
Added in contrasts on figure for consistency

```{r maleharm, fig.width=11.56944, fig.height=7.62500, fig.cap="Distribution of effect sizes, overall meta-analytic mean estimates and 95% confidence intervals (CIs) across species with different types of male harm towards females. Total effect sizes (n) and total number of studies (k) are provided for each level of Male Harm Type. Relevant contrasts between meta-analytic means are provided, along with 95% CIs and significance of contrast. Note that this includes all data. Removing outlier point from single study results in no different between harm type categories. "}

@@

contrast1 <- paste0("$\\beta_{contrast}$ = ", round(robust_model1.5$beta[2], digit = 2), ", 95% CI:", round(robust_model1.5$ci.lb[2], digit = 2), " to ", round(robust_model1.5$ci.ub[2], digit = 2), ", $\\textbf{p ", p_value(robust_model1.5$pval[2]), "}$")

@@

@@

harm_plot <- ggplot(data, aes(x = Harm_type, y = SMDH)) + 
              geom_violin(alpha = 0.2, aes(fill = Harm_type, colour = Harm_type)) + 
              #geom_point() + don't need this because we have geom_jitter. It will otherwise double plot points
              ylim(c(-2, 6.5)) + 
              geom_jitter(aes(x = Harm_type, y = SMDH, fill = Harm_type, colour = Harm_type, size = 1/sqrt(v_SMDH)),
                          width = 0.08, alpha = 0.2) + 
              theme_bw() + 
		          theme(legend.background = element_blank(),
			                     legend.key = element_blank()) + 
              labs(x = "Harm Type", 
                   y = "SMDH", 
                   size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
              scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
              guides(size = guide_legend(override.aes = list(linetype = 0))) + 
              scale_colour_discrete(guide = FALSE) +
              scale_fill_discrete(guide = FALSE) + 
              annotate('text', x = (seq(1, 3, 1)), y = 6.45, 
                       label= paste0("italic(n)==", robust_model1.5_2_PI$n), parse = TRUE, size = 3.5) +     
              annotate('text', x = (seq(1, 3, 1)), y = 6.15, 
                       label= paste0("italic(k)==", robust_model1.5_2_PI$nstudy), parse = TRUE, size = 3.5) +     
        	  	# 95 %CI: branches
        	    geom_errorbar(data = robust_model1.5_2_PI,  aes(x = moderator, y = Est, ymin = lwr.CI, ymax = up.CI), 
        	                  height = 0, show.legend = FALSE, size = 0.5, width = 0.05) +
              geom_point(data = robust_model1.5_2_PI, aes(x = moderator, y = Est, colour= moderator), size = 5)+
              geom_segment(aes(x = 1, y = 4.8, xend = 2, yend = 4.8), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
              geom_segment(aes(x = 1, y = 5.5, xend = 3, yend = 5.5), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) +
              #geom_segment(aes(x = 2, y = -1, xend = 3, yend = -1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both"))
              annotate('text', x = 1 + ((2-1) / 2), y = 5, label = TeX(contrast1), size = 4) + 
              annotate('text', x = 1 + ((3-1) / 2), y = 5.7, label = TeX(contrast2), size = 4) 
              #annotate('text', x = 2 + ((2-1) / 2), y = -1, label = TeX(contrast3), size = 2.5)

harm_plotvar <- ggplot(data_cvr, aes(x = Harm_type, y = logCVR)) + 
              geom_violin(alpha = 0.2, aes(fill = Harm_type, colour = Harm_type)) + 
              #geom_point() + don't need this because we have geom_jitter. It will otherwise double plot points
              ylim(c(-2, 2.5)) + 
              geom_jitter(aes(x = Harm_type, y = logCVR, fill = Harm_type, colour = Harm_type, size = 1/sqrt(v_logCVR)),
                          width = 0.08, alpha = 0.2) + 
              theme_bw() + 
		          theme(legend.background = element_blank(),
			                     legend.key = element_blank()) + 
              labs(x = "Harm Type", 
                   y = "ln CVR", 
                   size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{lnCVR}}}\\right)$")) +
              scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
              guides(size = guide_legend(override.aes = list(linetype = 0))) + 
              scale_colour_discrete(guide = FALSE) +
              scale_fill_discrete(guide = FALSE) + 
              annotate('text', x = (seq(1, 3, 1)), y = 2, 
                       label= paste0("italic(n)==", lncvr_results$n), parse = TRUE, size = 3.5) +     
              annotate('text', x = (seq(1, 3, 1)), y = 1.8, 
                       label= paste0("italic(k)==", lncvr_results$nstudy), parse = TRUE, size = 3.5) +     
        	  	# 95 %CI: branches
        	    geom_errorbar(data = lncvr_results,  aes(x = loc, y = estimate, ymin = lowerCL, ymax = upperCL), 
        	                  height = 0, show.legend = FALSE, size = 0.5, width = 0.05) +
              geom_point(data = lncvr_results, aes(x = loc, y = estimate), size = 5)

@@

p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH), colour = Harm_type)) + 
    geom_point(alpha = 0.6) + 
      theme_bw() + 
  labs(x = "Sexual Size Dimorphism (SSD) Index", 
	     y = "SMDH",
	  size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$"),
	  colour = "Male Harm Type") +
  scale_colour_discrete(labels = c("Both", "Direct", "Indirect")) +
	guides(size = guide_legend(direction = "vertical")) +
  annotate('text', x = -0.4, y = 4.5, label = TeX(contrast3top), size = 5) +
  annotate('text', x = -0.4, y = 4.2, label = TeX(contrast3bottom), size = 5) +
  annotate('text', x = -0.4, y = 3.9, label = TeX(contrast3bottom2, italic = TRUE), size = 5) +
  geom_abline(intercept = robust_model1.3_nonZ$beta[1], slope = robust_model1.3_nonZ$beta[2]) # Note using model1.3 for plotting because this is marginalised across Harm_type.

@@

sperm_plot = ggplot(sperm_data, aes(x = SCR.SCI, y = SMDH)) + 
              geom_violin(alpha = 0.1, aes(fill = SCR.SCI, colour = SCR.SCI)) + 
              geom_jitter(aes(x = SCR.SCI, y = SMDH, fill = SCR.SCI, colour = SCR.SCI, size = 1/sqrt(v_SMDH)),
                          width = 0.08, alpha = 0.1) + 
              ylim(c(-1.5, 6))+
              theme_bw() + 
		          theme(legend.background = element_blank(),
			                     legend.key = element_blank()) + 
              labs(x = "Sperm Competition Intensity", 
                   y = "SMDH", 
                   size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
              #scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
              guides(size = guide_legend(override.aes = list(linetype = 0))) + 
              scale_colour_discrete(guide = FALSE) +
              scale_fill_discrete(guide = FALSE) + 
              annotate('text', x = (seq(1, 2, 1)), y = 6, 
                       label= paste0("italic(n)==", robust_model1.7_PI$n[1:2]), parse = TRUE, size = 3.5) +     
              annotate('text', x = (seq(1, 2, 1)), y = 5.7, 
                       label= paste0("italic(k)==", robust_model1.7_PI$nstdy[1:2]), parse = TRUE, size = 3.5) +     
        	  	# 95 %CI: branches
        	    geom_errorbar(data = robust_model1.7_PI,  aes(x = moderator, y = Est, ymin = lwr.CI, ymax = up.CI), 
                            show.legend = FALSE, size = 0.5, width = 0.05) +
              geom_point(data = robust_model1.7_PI, aes(x = moderator, y = Est, colour= moderator), size = 5) +
              geom_segment(aes(x = 1, y = 5.35, xend = 2, yend = 5.35), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
  annotate('text', x = 1.5, y = 5, label = TeX(contrast_sperm), size = 3) + 
    annotate('text', x = 1.5, y = 4.6, label = TeX(contrast_sperm2), size = 3) + 
    annotate('text', x = 1.5, y = 4.2, label = TeX(contrast_sperm3), size = 3)

>>>>

```{r maleharm, fig.width=20.8, fig.height=7.4, fig.cap="Distribution of effect sizes, overall meta-analytic mean estimates and 95% confidence intervals (CIs) across species with different types of male harm towards females. A) Standardised Mean Difference with Heteroscedasticity correction (SMDH) and B) the log Coefficient of Variation (lnCVR). Total effect sizes (n) and total number of studies (k) are provided for each level of Male Harm Type. Relevant contrasts between meta-analytic means are provided, along with 95% CIs and significance of contrast. Note that this includes all data. Removing outlier point from single study results in no different between harm type categories. "}

@@

contrast1 <- paste0("$\\beta_{contrast}$ = ", round(robust_model1.5$beta[2], digit = 2), ", 95% CI:", round(robust_model1.5$ci.lb[2], digit = 2), " to ", round(robust_model1.5$ci.ub[2], digit = 2), ", $\\textbf{p =", p_value(robust_model1.5$pval[2]), "}$")

@@

contrast1v <- paste0("$\\beta_{contrast}$ = ", round(robust_model1_lnCVR_harm$beta[2], digit = 2), ", 95% CI:", round(robust_model1_lnCVR_harm$ci.lb[2], digit = 2), " to ", round(robust_model1_lnCVR_harm$ci.ub[2], digit = 2), ", $p =", p_value(robust_model1_lnCVR_harm$pval[2]), "$")

contrast2v <- paste0("$\\beta_{contrast}$ = ", round(robust_model1_lnCVR_harm$beta[3], digit = 2), ", 95% CI:", round(robust_model1.5$ci.lb[3], digit = 2), " to ", round(robust_model1_lnCVR_harm$ci.ub[3], digit = 2), ", p = ", p_value(robust_model1_lnCVR_harm$pval[3]))

@@

harm_plot <- ggplot(data, aes(x = Harm_type, y = SMDH)) + 
              geom_violin(alpha = 0.2, aes(fill = Harm_type, colour = Harm_type)) + 
              #geom_point() + don't need this because we have geom_jitter. It will otherwise double plot points
              ylim(c(-2, 6.5)) + 
              geom_jitter(aes(x = Harm_type, y = SMDH, fill = Harm_type, colour = Harm_type, size = 1/sqrt(v_SMDH)),
                          width = 0.08, alpha = 0.2) + 
              theme_classic() + 
		          theme(legend.background = element_blank(),
			                     legend.key = element_blank()) + 
              labs(x = "Harm Type", 
                   y = "SMDH", 
                   size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
              scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
              guides(size = guide_legend(override.aes = list(linetype = 0))) + 
              scale_colour_discrete(guide = FALSE) +
              scale_fill_discrete(guide = FALSE) + 
              annotate('text', x = (seq(1, 3, 1)), y = 6.45, 
                       label= paste0("italic(n)==", robust_model1.5_2_PI$n), parse = TRUE, size = 3.5) +     
              annotate('text', x = (seq(1, 3, 1)), y = 6.15, 
                       label= paste0("italic(k)==", robust_model1.5_2_PI$nstudy), parse = TRUE, size = 3.5) +     
        	  	# 95 %CI: branches
        	    geom_errorbar(data = robust_model1.5_2_PI,  aes(x = moderator, y = Est, ymin = lwr.CI, ymax = up.CI), 
        	                  height = 0, show.legend = FALSE, size = 0.5, width = 0.05) +
              geom_point(data = robust_model1.5_2_PI, aes(x = moderator, y = Est, colour= moderator), size = 5)+
              geom_segment(aes(x = 1, y = 4.8, xend = 2, yend = 4.8), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
              geom_segment(aes(x = 1, y = 5.5, xend = 3, yend = 5.5), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) +
              #geom_segment(aes(x = 2, y = -1, xend = 3, yend = -1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both"))
              annotate('text', x = 1 + ((2-1) / 2), y = 5, label = TeX(contrast1), size = 4) + 
              annotate('text', x = 1 + ((3-1) / 2), y = 5.7, label = TeX(contrast2), size = 4) 
              #annotate('text', x = 2 + ((2-1) / 2), y = -1, label = TeX(contrast3), size = 2.5)

lncvr_results$moderator <- c("both", "direct", "indirect")

harm_plotvar <- ggplot(data_cvr, aes(x = Harm_type, y = logCVR)) + 
              geom_violin(alpha = 0.2, aes(fill = Harm_type, colour = Harm_type)) + 
              #geom_point() + don't need this because we have geom_jitter. It will otherwise double plot points
              ylim(c(-2, 2.5)) + 
              geom_jitter(aes(x = Harm_type, y = logCVR, fill = Harm_type, colour = Harm_type, size = 1/sqrt(v_logCVR)),
                          width = 0.08, alpha = 0.2) + 
              theme_classic() + 
		          theme(legend.background = element_blank(),
			                     legend.key = element_blank()) + 
              labs(x = "Harm Type", 
                   y = "log Coefficient of Variation (lnCVR)", 
                   size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{lnCVR}}}\\right)$")) +
              scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
              guides(size = guide_legend(override.aes = list(linetype = 0))) + 
              scale_colour_discrete(guide = FALSE) +
              scale_fill_discrete(guide = FALSE) + 
              annotate('text', x = (seq(1, 3, 1)), y = 2, 
                       label= paste0("italic(n)==", lncvr_results$n), parse = TRUE, size = 3.5) +     
              annotate('text', x = (seq(1, 3, 1)), y = 1.8, 
                       label= paste0("italic(k)==", lncvr_results$nstudy), parse = TRUE, size = 3.5) +     
        	  	# 95 %CI: branches
        	    geom_errorbar(data = lncvr_results,  aes(x = loc, y = estimate, ymin = lowerCL, ymax = upperCL), 
        	                  height = 0, show.legend = FALSE, size = 0.5, width = 0.05) +
              geom_point(data = lncvr_results, aes(x = loc, y = estimate, colour= moderator), size = 5) +
              geom_segment(aes(x = 1, y = 1, xend = 2, yend = 1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
              geom_segment(aes(x = 1, y = 1.3, xend = 3, yend = 1.3), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) +
              #geom_segment(aes(x = 2, y = -1, xend = 3, yend = -1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both"))
              annotate('text', x = 1 + ((2-1) / 2), y = 1.1, label = TeX(contrast1v), size = 4) + 
              annotate('text', x = 1 + ((3-1) / 2), y = 1.4, label = TeX(contrast2v), size = 4)

@@

p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH), colour = Harm_type)) + 
    geom_point(alpha = 0.6) + 
      theme_classic() + 
  labs(x = "Sexual Size Dimorphism (SSD) Index", 
	     y = "SMDH",
	  size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$"),
	  colour = "Male Harm Type") +
  scale_colour_discrete(labels = c("Both", "Direct", "Indirect")) +
	guides(size = guide_legend(direction = "vertical")) +
  annotate('text', x = -0.4, y = 4.5, label = TeX(contrast3top), size = 5) +
  annotate('text', x = -0.4, y = 4.2, label = TeX(contrast3bottom), size = 5) +
  annotate('text', x = -0.4, y = 3.9, label = TeX(contrast3bottom2, italic = TRUE), size = 5) +
  geom_abline(intercept = robust_model1.3_nonZ$beta[1], slope = robust_model1.3_nonZ$beta[2]) # Note using model1.3 for plotting because this is marginalised across Harm_type.

@@

sperm_plot = ggplot(sperm_data, aes(x = SCR.SCI, y = SMDH)) + 
              geom_violin(alpha = 0.1, aes(fill = SCR.SCI, colour = SCR.SCI)) + 
              geom_jitter(aes(x = SCR.SCI, y = SMDH, fill = SCR.SCI, colour = SCR.SCI, size = 1/sqrt(v_SMDH)),
                          width = 0.08, alpha = 0.1) + 
              ylim(c(-1.5, 6))+
              theme_classic() + 
		          theme(legend.background = element_blank(),
			                     legend.key = element_blank()) + 
              labs(x = "Sperm Competition Intensity", 
                   y = "SMDH", 
                   size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
              #scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
              guides(size = guide_legend(override.aes = list(linetype = 0))) + 
              scale_colour_discrete(guide = FALSE) +
              scale_fill_discrete(guide = FALSE) + 
              annotate('text', x = (seq(1, 2, 1)), y = 6, 
                       label= paste0("italic(n)==", robust_model1.7_PI$n[1:2]), parse = TRUE, size = 3.5) +     
              annotate('text', x = (seq(1, 2, 1)), y = 5.7, 
                       label= paste0("italic(k)==", robust_model1.7_PI$nstdy[1:2]), parse = TRUE, size = 3.5) +     
        	  	# 95 %CI: branches
        	    geom_errorbar(data = robust_model1.7_PI,  aes(x = moderator, y = Est, ymin = lwr.CI, ymax = up.CI), 
                            show.legend = FALSE, size = 0.5, width = 0.05) +
              geom_point(data = robust_model1.7_PI, aes(x = moderator, y = Est, colour= moderator), size = 5) +
              geom_segment(aes(x = 1, y = 5.35, xend = 2, yend = 5.35), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
  annotate('text', x = 1.5, y = 5, label = TeX(contrast_sperm), size = 3) + 
    annotate('text', x = 1.5, y = 4.6, label = TeX(contrast_sperm2), size = 3) + 
    annotate('text', x = 1.5, y = 4.2, label = TeX(contrast_sperm3), size = 3)
